|

### 2019-09-02 paper.Rmd
Adding in last two examples.

### Needle in a haystack

### Non-linear boundaries

>>>>

### Needle in a haystack
We use the pollen data as an example for a hidden feature generally occluded in projections. This 1986 Exposition's dataset was made by David Coleman of RCA Labs. The artificially generated data is comprised of 3848 observations on 5 variables. We center and scale each variable of the dataset and run a slice tour with a thin slice ($\epsilon = 0.0005$). Selected views are shown in the first two plots in Figure \ref{fig:pollen}, indicating the presence of an interesting feature hidden in the center. We next zoom in on the center of the distribution and consider a thicker slice ($\epsilon = 0.005$) to uncover the hidden structure, shown in the last two plots of Figure \ref{fig:pollen}.

\begin{figure*}[ht]
\centerline{\includegraphics[width=0.2\textwidth]{gifs/png/pollen-007.png}
\hspace{5mm}
\includegraphics[width=0.2\textwidth]{gifs/png/pollen-092.png}
\hspace{5mm}
\includegraphics[width=0.2\textwidth]{gifs/png/pollen-zoom-075.png}
\hspace{5mm}
\includegraphics[width=0.2\textwidth]{gifs/png/pollen-zoom-018.png}
}
\caption{Different slices through the pollen dataset. The first two plots have slice volume $\epsilon = 0.0005$, the last two plots zoom in on the center and have increased volume $\epsilon = 0.005$.}
\label{fig:pollen}
\end{figure*}

### Non-linear boundaries
XXX say something about this dataset [@sam.11271]

Selected views from a slice tour of the scaled and centered data, and with large slice volume $\epsilon = 0.15$ are shown in Figure \ref{fig:wine}. The slices allow to clearly see the non-linearity of the boundary between the green and orange group. The first view also shows a non-linear boundary of the purple group, which interestingly does not appear at all in the second slice shown here.

\begin{figure*}[ht]
\centerline{\includegraphics[width=0.2\textwidth]{gifs/png/wine-029.png}
\hspace{5mm}
\includegraphics[width=0.2\textwidth]{gifs/png/wine-042.png}
\hspace{5mm}
\includegraphics[width=0.2\textwidth]{gifs/png/wine-049.png}
\hspace{5mm}
\includegraphics[width=0.2\textwidth]{gifs/png/wine-100.png}
}
\caption{Different slices through the wine dataset.}
\label{fig:wine}
\end{figure*}
